Application of Machine Learning to Increase the Efficiency of the Global Search Algorithm for Solving Multicriterial Problems\thanks{This research was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-06-10 2023/NUMTA/Full paper/NUMTA_2023_MCO.tex
fix

Problems with greater dimension were solved in the third series of experiments. Multiextremal functions of the class GKLS \cite{Gaviano2003} have been chosen as partial criteria of the MMCO problems.  In global optimization this class is widely used for testing global search algorithms. Bi-criteria problems of dimensions $n=3$ and $n=4$ were considered. Weight coefficients were chosen as nodes of a uniform grid in the domain defined by the conditions (\ref{eq:06}) with number of nodes equal to 200 in 3-dimensional case and to 50 for $n=4$. 100 MMCO problems were participated in the experiment for each dimension. ALR-R and ALR-SP used the same parameter   $r=4.5$.  ALR-SP applied the parameter $\beta=0.05$ for the dimension $n=3$ and $\beta=0.025$ in the case of $n=4$.  Running of each evolutionary method was repeated 10 times and results were averaged.

>>>>

Problems with greater dimension were solved in the third series of experiments. Multiextremal functions of the class GKLS \cite{Gaviano2003} have been chosen as partial criteria of the MMCO problems.  In global optimization this class is widely used for testing global search algorithms. Bi-criteria problems of dimensions $n=3$ and $n=4$ were considered. Weight coefficients were chosen as nodes of a uniform grid in the domain defined by the conditions (\ref{eq:06}) with number of nodes equal to 200 in 3-dimensional case and to 50 for $n=4$. 100 MMCO problems were participated in the experiment for each dimension. AGS-R and AGS-SP used the same parameter $r=4.5$. AGS-SP applied the parameter $\beta=0.05$ for the dimension $n=3$ and $\beta=0.025$ in the case of $n=4$.  Running of each evolutionary method was repeated 10 times and results were averaged.
